---
title: "Statistical Concepts- Assignment2"
author: "Hilal Sankari"
format: 
    html:
      code-line-numbers: true
      df-print: paged

---
```{r}
# Load data
random_vars <- readRDS("C:/Users/user/Documents/TUHH/Causal/Causal_Data_Science_Data/random_vars.rds")
```
# **Part1**
#### **Set age and icome sets**
```{r}
age_var <- random_vars$age
income_var <- random_vars$income
```
# **Part1.1**
```{r}
# 1.Expected Value
expected_value_age <- sum(age_var) / length(age_var)
expected_value_income <- sum(income_var) / length(income_var)
```
#### **Part1.1 Results**
```{r}
#| code-fold: true
cat("Expected age Value:", expected_value_age, "\n")
cat("Expected income Value:", expected_value_income, "\n")
```
# **Part1.2**
```{r}
#2.Variance
mean_value_age <- mean(age_var)
mean_value_income <- mean(income_var)
variance_value_age <- sum((age_var - mean_value_age)^2) / (length(age_var) - 1)
variance_value_income<- sum((income_var - mean_value_income)^2) / (length(income_var) - 1)
```
#### **Part1.2 Results**
```{r}
#| code-fold: true
cat("Variance age Value:", variance_value_age, "\n")
cat("Variance income Value:", variance_value_income, "\n")
```
# **Part1.3**
```{r}
#3.Standard Deviation
standard_deviation_value_age <- sqrt(variance_value_age)
standard_deviation_value_income <- sqrt(variance_value_income)
```
#### **Part1.3 Results**
```{r}
#| code-fold: true
cat("Standard Deviation age Value:", standard_deviation_value_age, "\n")
cat("Standard Deviation income Value:", standard_deviation_value_income, "\n")
```
# **Part2**
#### **Comparing Standard Deviation**
::: {.callout-important appearance="minimal"}
Comparing standard deviations directly is most meaningful when the variables are measured in the same units and have similar scales. In the case of age and income, these two variables have different units and different scales. Therefore, comparing their standard deviations directly may not provide meaningful insights.
:::
# **Part3.1**
#### **Covariance**
```{r}
covariance_value <- sum((age_var - mean_value_age) * (income_var - mean_value_income)) / length(age_var)
```
#### **Part3.1 Results**
```{r}
#| code-fold: true
cat("Covariance Value:", covariance_value, "\n")
```
# **Part3.2**
#### **Correlation**
```{r}
correlation_value <- covariance_value / (standard_deviation_value_age*standard_deviation_value_income)
```
#### **Part3.1 Results**
```{r}
#| code-fold: true
cat("Correlation Value:", correlation_value, "\n")
```
# **Part4**
::: {.callout-important appearance="minimal"}
The correlation coefficient's standardized scale makes it more intuitive for comparison. The fact that it ranges from -1 to 1 allows for a clear understanding of the strength and direction of the relationship.
:::
# **Part5.1**
#### **conditional expected value, E[income|age<=18]**
```{r}
subset_data1 <- subset(random_vars, age <= 18)
conditional_expected_value1 <- mean(subset_data1$income)
```
#### **Part5.1 Results**
```{r}
#| code-fold: true
cat("Conditional Expected Value of Income for age <= 18:", conditional_expected_value1, "\n")
```
# **Part5.2**
#### **conditional expected value, E[income|age<=[18,65)]**
```{r}
subset_data2 <- subset(random_vars, age >= 18 & age < 65)
conditional_expected_value2 <- mean(subset_data2$income)
```
#### **Part5.2 Results**
```{r}
#| code-fold: true
cat("Conditional Expected Value of Income for age in [18, 65):", conditional_expected_value2, "\n")
```
# **Part5.2**
#### **conditional expected value, E[income|age>=65]**
```{r}
subset_data3 <- subset(random_vars, age >= 65)
conditional_expected_value3 <- mean(subset_data3$income)
```
```{r}
#| code-fold: true
cat("Conditional Expected Value of Income for age >= 65:", conditional_expected_value3, "\n")
```