---
title: "Regression and Statistical Inference - Assignment 3"
author: "Hilal Sankari"
format: 
    html:
      code-line-numbers: true
      df-print: paged

---
----
```{r}

# Load Libraries
library(dplyr)
library(modelr)
```
```{r}
# Load data
# Read data set. Check what folder/path your data is in. 
car_data <- readRDS("C:/Users/user/Documents/TUHH/Causal/Causal_Data_Science_Data/car_prices.rds")
```
# **Part1**
#### **Number of rows and columns**
```{r}
rows_columns <- dim(car_data)
rows <- rows_columns[1]
columns <- rows_columns[2]
```
#### **Number of rows and columns**
```{r}
#| code-fold: true
cat("Number of rows:", rows, "\n")
cat("Number of columns:", columns, "\n")
```
# **Part2**
```{r}
# Extract column names for each data frame in the list
column_names_list <- lapply(car_data, colnames)
first_element <- head(car_data$carwidth, 1)
cat("the type of carwidth is", typeof(first_element), "\n")
first_element <- head(car_data$carbody, 1)
cat("the type of carbody is", typeof(first_element), "\n")
print("There are two types: char and double")
```
::: {.callout-important appearance="minimal"}
Numeric types like double are ideal for quantitative information, while strings and char are useful for textual and categorical information. The key is to accurately represent the real-world attributes of the cars and associated market data in your program.
:::
# **Part3**
#### **Linear Regression**
```{r}
glimpse(car_data)
car_data[] <- lapply(car_data, as.numeric)
car_data %>%
  # Calculate the correlation matrix
  cor() %>% 
  # Round the correlation values to 2 decimal places
  round(2) %>% 
  # Extract the lower triangular part of the matrix
  Matrix::tril()
```
# **Part4.1**
#### **explain what data type it is and what values it can take on**
```{r}
first_element <- head(car_data$enginesize, 1)
min_value <- min(car_data$enginesize)
max_value <- max(car_data$enginesize)
cat("The regressor chosen is the enginesize and it has a type of ", typeof(first_element)," and it ranges between" ,min_value," and ", max_value ,"\n")
```
# **Part4.2**
::: {.callout-important appearance="minimal"}
It affects the price with a percentage of  89% so it has a big effect, and it effects it with a positive correlation so when the engine size increases the price increases (in a proportional manner).
:::
# **Part4.3**
::: {.callout-important appearance="minimal"}
As mentioned it affects the price with a 89% , so it does affect it significantly
:::
# **Part5**
#### **Seat Heating**
```{r}
cardata_with_seat_heating <- car_data %>%
  mutate(seat_heatingTRUE = sample(c(TRUE, FALSE), size = nrow(car_data), replace = TRUE))

# Check the distribution of seat_heatingTRUE
table(cardata_with_seat_heating$seat_heatingTRUE)

# Run the regression again
linear_model <- lm(price ~ seat_heatingTRUE, data = cardata_with_seat_heating)

# Print the summary of the linear model
summary(linear_model)
```
::: {.callout-important appearance="minimal"}
If all the values are assigned as true there will be no variability, and which can lead to issues in regression analysis, including collinearity problems and difficulties in estimating coefficients.
:::