---
title: "Directed Acyclic Graphs - Assignment 5"
author: "Hilal Sankari"
format: 
    html:
      code-line-numbers: true
      df-print: paged

---
```{r}
# Load necessary libraries
library(tidyverse)    # For data manipulation and visualization
library(dagitty)      # For working with Directed Acyclic Graphs (DAGs)
library(ggdag)        # For DAG visualization with ggplot2
```
# **Part1**
#### **Draw DAG**
```{r}
# Construct DAG for Sales Example
sales_graph <- dagify(
  product_sales ~ parking_capacity,
  product_sales ~ store_location,
  parking_capacity ~ store_location, # store_location acts as the confounding variable
  labels = c(
    "product_sales" = "Product Sales",
    "parking_capacity" = "Parking \n Capacity",
    "store_location" = "Store Location"
  )
)
ggdag(sales_graph, use_labels = "label", text = FALSE)
```
# **Part2**

#### **Read and Explore Data**
```{r}
# Load the customer satisfaction data
customer_data <- readRDS('C:/Users/user/Documents/TUHH/Causal/Causal_Data_Science_Data/customer_sat.rds')
# Explore the data
head(customer_data)
```
# **Part2.1**

#### **Fit a regression model: satisfaction ~ follow-ups**
```{r}
## Simple linear Regression ##
model_unadjusted <- lm(satisfaction ~ follow_ups, data = customer_data)

summary(model_unadjusted)
```
# **Part2.2**

#### **Fit a regression model: satisfaction ~ follow-ups + subscription**
```{r}
## Multiple Linear Regression
model_adjusted <- lm(satisfaction ~ follow_ups + subscription, data = customer_data)

summary(model_adjusted)
```
# **Part3**

#### **Compare coefficients from the two models**
```{r}
coef_comparison <- data.frame(
  Model = c("Model 1", "Model 2"),
  Intercept = c(coef(model_unadjusted)[1], coef(model_adjusted)[1]),
  FollowUps = c(coef(model_unadjusted)[2], coef(model_adjusted)[2]),
  PremiumPlus = c(0, coef(model_adjusted)[grep("subscription_typePremium\\+", names(coef(model_adjusted)))]),
  Elite = c(0, coef(model_adjusted)[grep("subscription_typeElite", names(coef(model_adjusted)))])
)

print(coef_comparison)
```
::: {.callout-important appearance="minimal"}
Model 2 exhibits a lower baseline satisfaction compared to Model 1, attributed to its reduced intercept.
Incorporating subscription information altered the direction of the association between Follow-ups and satisfaction, shifting it from negative to positive.
PremiumPlus subscription has a positive influence on satisfaction, while there is no supplementary effect observed for the Elite subscription level.
:::

# **Part4**

#### **Visualise Data**

```{r}
### Simpson's Paradox: Subscription as the Confounding Variable ###


## Without conditioning on subscription

simps_not_cond <- ggplot(customer_data, aes(x = follow_ups, y = satisfaction)) +
  geom_point(alpha = 0.8) +
  stat_smooth(method = "lm", se = F) +
  labs(title = "Relationship between Follow-ups and Satisfaction",
       x = "Follow-up Calls",
       y = "Customer Satisfaction") +
  theme_minimal() +
  theme(legend.position = "right")


## Conditioning on subscription

simps_cond <- ggplot(customer_data, aes(x = follow_ups, y = satisfaction, color = subscription)) +
  geom_point(alpha = 0.8) +
  stat_smooth(method = "lm", se = F, size = 1) +
  labs(title = "Relationship between Follow-ups and Satisfaction by Subscription Type",
       x = "Follow-up Calls",
       y = "Customer Satisfaction",
       color = "Subscription Type") +
  theme_minimal() +
  theme(legend.position = "right")
```
#### **Part 4 Results**
```{r}
#| code-fold: true
simps_not_cond
simps_cond
```