---
title: "Randomized Controlled Trials - Assignment 6"
author: "Hilal Sankari"
format: 
    html:
      code-line-numbers: true
      df-print: paged

---
# **Part1**
```{r}
# Load necessary libraries
library(ggplot2)
```
```{r}
customer_data <- readRDS("C:/Users/user/Documents/TUHH/Causal/Causal_Data_Science_Data/abtest_online.rds")
customer_data
```
```{r}
compare_purchase_amount <- 
  ggplot(customer_data, 
         aes(x = chatbot, 
             y = purchase_amount, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "purchase_amount", title = "Difference in purchase amount")+
  scale_x_discrete(labels = c("Not Treated","Treated"))
compare_previous_visit <- 
  ggplot(customer_data, 
         aes(x = chatbot, 
             y = previous_visit, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "previous_visit", title = "Difference in previous visit")+
  scale_x_discrete(labels = c("Not Treated","Treated"))
compare_mobile_device <- 
  ggplot(customer_data, 
         aes(x = chatbot, 
             y = mobile_device, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "mobile_device", title = "Difference in mobile device")+
  scale_x_discrete(labels = c("Not Treated","Treated"))
compare_purchase <- 
  ggplot(customer_data, 
         aes(x = chatbot,
             y = purchase, 
             color = as.factor(chatbot))) +
  stat_summary(geom = "errorbar", 
               width = .5,
               fun.data = "mean_se", 
               fun.args = list(mult=1.96),
               show.legend = F) +
  labs(x = NULL, y = "purchase", title = "Difference in purchase")+
  scale_x_discrete(labels = c("Not Treated","Treated"))
```
```{r}
# Plot 
compare_purchase_amount
compare_previous_visit
compare_mobile_device
compare_purchase
```
# **Part2**
```{r}
lm1 <- lm(purchase ~ chatbot, data = customer_data)
summary(lm1)
lm2 <- lm(purchase_amount ~ chatbot, data = customer_data)
summary(lm2)
```
# **Part3**
```{r}
lm_mod1 <- lm(purchase ~ chatbot * mobile_device, data = customer_data)
summary(lm_mod1)
lm_mod2 <- lm(purchase_amount ~ chatbot * mobile_device, data = customer_data)
summary(lm_mod2)
```
# **Part4**
```{r}
# Logistic regression model
logistic_model <- glm(purchase ~ chatbot, family = binomial(link = 'logit'), data = customer_data)

# Display summary of the logistic regression model
summary(logistic_model)
```
::: {.callout-important appearance="minimal"}
The chatbotTRUE coefficient is of particular interest. Since it has a negative estimate, it suggests that, compared to when the chatbot is not present, the presence of the chatbot is associated with a decrease in the log-odds of making a purchase. The p-value being less than 0.001 indicates that this effect is statistically significant.
In simpler terms, the model suggests that customers are less likely to make a purchase when the chatbot is present, and this effect is unlikely to be due to random chance.
Lastly, the null and residual deviances and the AIC (Akaike Information Criterion) are model fit statistics. Lower AIC values generally indicate better-fitting models. In this case, the residual deviance is 1273.3 on 998 degrees of freedom, and the AIC is 1277.3
:::