---
title: "Regression Discontinuity - Assignment 10"
author: "Hilal Sankari"
format: 
    html:
      code-line-numbers: true
      df-print: paged

---
```{r}
# Load necessary libraries
library(dplyr)
library(ggplot2)
library(rddensity)
```
```{r}
# Read data for the current campaign
current_campaign_data <- readRDS("C:/Users/user/Documents/TUHH/Causal/Causal_Data_Science_Data/coupon.rds")
# Read data for the different past campaign
past_campaign_data <- readRDS("C:/Users/user/Documents/TUHH/Causal/Causal_Data_Science_Data/shipping.rds")
```
```{r}
# [1] Regression Discontinuity Design Sensitivity Analysis ----

# Define cut-off
cutoff_point <- 60

# Bandwidths
original_bandwidth <- cutoff_point + c(-5, 5)
half_bandwidth <- cutoff_point + c(-5, 5) / 2
double_bandwidth <- cutoff_point + c(-5, 5) * 2
```
#### **Function to run the regression discontinuity design analysis**
```{r}
run_rdd_analysis <- function(data, bandwidth) {
  data_below <- data %>% filter(days_since_last >= bandwidth[1] & days_since_last < cutoff_point)
  data_above <- data %>% filter(days_since_last >= cutoff_point & days_since_last <= bandwidth[2])
  data_combined <- bind_rows(data_above, data_below)
  
  lm_result <- lm(purchase_after ~ days_since_last_centered + coupon, data_combined)
  
  model_below <- lm(purchase_after ~ days_since_last, data_below)
  model_above <- lm(purchase_after ~ days_since_last, data_above)
  
  y0 <- predict(model_below, tibble(days_since_last = cutoff_point))
  y1 <- predict(model_above, tibble(days_since_last = cutoff_point))
  
  late_estimate <- y1 - y0
  return(list(LATE = late_estimate, Summary = summary(lm_result)))
}
```
#### **Run the analysis with the original bandwidth**
```{r}
original_bandwidth_results <- run_rdd_analysis(current_campaign_data, original_bandwidth)
```
#### **Run the analysis with half the bandwidth**
```{r}
half_bandwidth_results <- run_rdd_analysis(current_campaign_data, half_bandwidth)
```
#### **Run the analysis with double the bandwidth**
```{r}
double_bandwidth_results <- run_rdd_analysis(current_campaign_data, double_bandwidth)
```
```{r}
# Print the results for the original bandwidth
cat("Original Bandwidth:\n")
cat("LATE:", original_bandwidth_results$LATE, "\n")
print(original_bandwidth_results$Summary)

# Print the results for half the bandwidth
cat("\nHalf the Bandwidth:\n")
cat("LATE:", half_bandwidth_results$LATE, "\n")
print(half_bandwidth_results$Summary)

# Print the results for double the bandwidth
cat("\nDouble the Bandwidth:\n")
cat("LATE:", double_bandwidth_results$LATE, "\n")
print(double_bandwidth_results$Summary)
```
::: {.callout-important appearance="minimal"}
The observed LATE is consistently stable across all three bandwidth choices, implying a consistently positive impact of the coupon variable on purchase_after.
While the LATE estimate is slightly reduced for the half bandwidth, indicating a more cautious assessment, it slightly increases for the double bandwidth, suggesting a potential broader impact on individuals farther from the cutoff point.
The choice of bandwidth significantly influences the treatment (couponTRUE) effect estimation, with coefficients showing variation in response to changes in bandwidth.
:::
```{r}
# [2] Different Past Campaign ----

rdd_density_results <- rddensity(past_campaign_data$purchase_amount, c = 30)
summary(rdd_density_results)
```
::: {.callout-important appearance="minimal"}
Significant evidence of manipulation around the cut-off point (c=30) is indicated by the manipulation tests. P-values of the robust T-statistic are nearly zero, implying systematic changes in the observed density of the purchase_amount variable near the cut-off. The order of estimation and bias differs on each side, suggesting a lack of smoothness or continuity in the observed changes. Further evidence of non-random behavior around the cut-off is provided by the p-values of binomial tests. Based on the manipulation testing results, the purchase_amount variable may not be suitable as a running variable for an RDD with a cut-off at 30€.
:::

```{r}
# Plot to confirm that purchase_amount could not be used as a running variable at 30
ggplot(past_campaign_data, aes(x = purchase_amount)) +
  geom_histogram(binwidth = 5, fill = "pink", color = "black") +
  geom_vline(xintercept = 30, color = "blue", linetype = "dashed") +
  xlab("Purchase Amount (€)") +
  ylab("Number of Purchases") +
  theme_minimal()
```